---
title: "Data overview"
author: "Justina Laškovaitė-Kolinienė"
date: "20/12/2022"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

```{r load-packages, include=FALSE}
library(knitr)
#install.packages("ggplot2", dependencies = TRUE)
library("ggplot2")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data overview

There are 1 000 000 rows and 17 columns in the document. So here you can see short summary of every column of the document. For example: min and max values, means and medians and also how many NA values there are. 

```{r df}
df <- read.csv(file = "C:/Users/Justina/Desktop/DVDA_magistras/I_kursas/LAB5/KTU-DVDA-PROJECT/project/1-data/train_data.csv")
df <- as.data.frame(df)
dim(df)
summary(df)
```

## First plot

As we can see in the plot below, loan amount does not depends on yearly income. 

```{r Current Loan Amount and Yearly Income, echo=FALSE}
ggplot(df, aes(x = amount_current_loan, y = yearly_income)) + geom_point(colour = "black") 
```

## Second plot

In the plot below we can inspect the relationship between Monthly Debt Amount and Years of Credit History. 

```{r Monthly Debt Amount and Years of Credit History, echo=FALSE}
ggplot(df, aes(x = monthly_debt, y = years_credit_history)) + geom_point(colour = "black") 
```